### 2014-06-03 manuscript/latitudepaper.tex
Started fleshing out results.

The scaling relationships of many food-web properties changed across latitude.
(need to look up difference between change in slope and change in int.) Mean
trophic level scaled with species but not connectance and had both slope and
intercept effects of latitude and ecotype. Maximum trophic level scaled with
both species-richness and connectance, with the species-richness relationship
having both slope and intercept effects of latitude while the connectance
relationship had both slope and intercept effects of ecotype. Similarly, the
scaling of generality with species-richness has both slope and intercept
effects of latitude, as well as an intercept effect of ecotype.

>>>>

Most food-web properties scaled with species-richness and/or connectance, and many of these relationships changed across latitude.
In the best-fit models, the percentages of species that were top predators, intermediate consumers, basal resources, herbivores, and omnivores did not significantly covary with either species-richness or connectance.
Mean trophic level scaled with species richness, mean shortest path scaled with connectance, and all other properties scaled with both species richness and connectance.

The strength of the scaling relationship between mean trophic level and species richness decreased with increasing latitude ($\beta=-0.008$,$p<0.001$). In addition, different ecosystem types had both different intercept trophic levels (except for lakes, which did not differ from estuaries) and different scaling relationships with species-richness (again except for lakes). Scaling of mean trophic level with species richness was strongest for estuarine food webs ($\beta=0.616$,$p<0.001$; intercept) and was progressively weaker for lake webs, stream webs, terrestrial webs, and marine webs.

Mean shortest path length decreased with increasing connectance ($\beta=-1.269$,$p=0.016$), and this relationship did not change with latitude. Although path length increased with latitude ($\beta=0.005$,$p=0.045$), the best-fitting model did not include a change to the scaling relationship with latitude. Different ecosystems, however, both had different intercept path lengths and different scaling relationships with connectance.

Mean and SD of vulnerability and SD of generality scaled with both species richness and connectance, but none of these scaling relationships varied either with latitude or with ecosystem type.

SD of links per species scaled with both species richness and connectance. Neither scaling relationship varied with latitude, and only the relationship with connectance varied across ecosystem types. LinkSD increased with increasing connectance ($\beta=0.999$,$p<0.001$), and this relationship was strongest for terrestrial and estuarine webs and weaker for marine, lake, and stream webs.

Similarly, mean links per species did not vary with latitude but did across ecosystem types. Streams had the highest mean L/S, followed by lakes, marine webs, terrestrial webs, and estuaries.

Gen, Max TL.
